From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-21 paper.tex
Minnor changes
Formatting

Six children (3 boys and 3 girls with ages 5 to 6) were enrolled for this study.
The study took place at school, in a separate room (the computer
lab). The participants were chosen by the teacher, and would come one after the
other for a face-to-face interaction with a {\sc Nao} robot (the duration has $\mu:
19.59$, $SD:1.58$).

The experiment is organized in rounds of writing: during a typical round, the
child requests the robot to write something (a single letter, a number or a full
word), and pushes a tactile tablet (equipped with a custom application that we
developed) towards the robot; the robot writes on the tablet by mimicking the
writing gesture (but without actually physically touching the tablet); the child
then pull back the tablet, corrects the robot's attempt by writing him/herself
on top or next to the robot's writing, and ``send'' his/her demonstration to the
robot by pressing a small button on the tablet. The robot learns from this
demonstration and tries again. The child continues the turn-taking until he/she
decides to train the robot on another word. Details on the rationale and
implementation of this study can be found in~\cite{Hood:2015}.

In this case, the number of rounds performed by each subject ($\mu: 12,16$, $SD:2.61$) 
varies depending on the interaction time, their ability writing and the easiness of use.
The number of rounds has a .

Besides, once per interaction, the robot did interrupt the handwriting task to
propose to tell a funny story. The story-telling lasted for 1 min. 58 sec., 
and the turn-based hand-writing task continued afterwards. The
intended purpose of the story-telling episode was to locally trigger a different
set of gaze behaviors.

@@

For instance, subjects 1,4 and 5 despite the fact that the tracking accuracy is
in the average, the bad precision in the captured VFoA suggests that such
children are highly likely to modify the gaze direction without head movement
intervention reducing dramatically the overlap between the manually annotated 
focus of attention and robot's computed focus of attention.

>>>>

Six children (ages 5 to 6, 3 boys, 3 girls) were enrolled for this study.
The study took place at school, in a separate room (the computer
lab). The participants were chosen by the teacher, and would come one after the
other for a face-to-face interaction with a {\sc Nao} robot (average duration:
19.6 min, $SD:1.58$).

The experiment is organized in rounds of writing: during a typical round, the
child requests the robot to write something (a single letter, a number or a full
word), and pushes a tactile tablet (equipped with a custom application that we
developed) towards the robot; the robot writes on the tablet by mimicking the
writing gesture (but without actually physically touching the tablet); the child
then pull back the tablet, corrects the robot's attempt by writing him/herself
on top or next to the robot's writing, and ``send'' his/her demonstration to the
robot by pressing a small button on the tablet. The robot learns from this
demonstration and tries again. The child continues the turn-taking until he/she
decides to train the robot on another word. In total, the children performed in
average 12.16 ($SD:2.61$) rounds of writing.

Besides, once per interaction, the robot interrupts the handwriting task to
propose to tell a story (that lasted for about 2 min), and the turn-based
hand-writing task continued afterwards. The intended purpose of the
story-telling episode was to locally trigger a different set of gaze behaviors.

Details on the rationale and implementation of this experiment can be found
in~\cite{Hood:2015}.

@@

For instance, subjects 1,4 and 5 despite the fact that the tracking accuracy is
in the average, the bad precision in the captured VFoA suggests that such
children are highly likely to modify the gaze direction without head movement
intervention reducing dramatically the overlap between the manually annotated 
focus of attention and robot's computed focus of attention. And in consequence,
increasing the standard deviation.
